Modified Silver Ion Chroma

### 2021-01-19 modified_silver_ion_chroma_2.Rmd
added plotly and knitted

---
title: "Modified Silver Ion Chroma"
author: "Tristan Caro"
date: "1/18/2021"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

@@

Following the success of [1️⃣**Modified Ag-ion SPE 1**](https://www.notion.so/Modified-Ag-ion-SPE-1-846ff2a886094428bd8effbb9f86e8b6), and comments from Seb and Jamie, we have further refined the ideal silver ion separation for FAMEs. Now, we are testing separation of FAMEs derived from free fatty acids ("F4s") donated by Jamie. The free FAs were derivatized to FAMEs using the BF3/MeOH method. In short:

@@

## Results

```{r, include = FALSE}
# Libraries
library(tidyverse)
library(plotly)
library(ggrepel)

@@

>>>>

---
title: "Modified Silver Ion Chroma"
author: "Tristan Caro"
date: "1/18/2021"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
---

@@

Following the tentative success of [1️⃣**Modified Ag-ion SPE 1**](https://www.notion.so/Modified-Ag-ion-SPE-1-846ff2a886094428bd8effbb9f86e8b6), and comments from Seb and Jamie, we have further refined the ideal silver ion separation for FAMEs. Now, we are testing separation of FAMEs derived from free fatty acids ("F4s") donated by Jamie. The free FAs were derivatized to FAMEs using the BF3/MeOH method. In short:

@@

## Data Proc and Cleanup

```{r}
# Libraries
library(tidyverse)
library(plotly)
library(ggrepel)

@@

```{r, warning = FALSE}
# Data cleanup
results <- all_data %>% 
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0) %>% 
  # major compound groups
  mutate(
    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor()
  )

results <- results %>% 
  mutate(saturation = case_when(
    str_detect(`Peak Name`, "OH") ~ "n0 hydroxy",
    str_detect(`Peak Name`, "cyclo") ~ "n0 cyclo",
    str_detect(`Peak Name`, ":0") ~ "n0",
    str_detect(`Peak Name`, ":2") ~ "n2 cis",
    str_detect(`Peak Name`, "cis") ~ "n1 cis",
    str_detect(`Peak Name`, "trans") ~ "n1 trans",
    str_detect(`Peak Name`, "PAIBE") ~ "PAIBE"
    )
  )
```

## Overview Plot

Most compounds derivatized from the free fatty acid fraction (F4) of Jamie's Boulder soil sample are saturated FAMEs or not readily identifiable by mass spec. For clarity, sterols, alkanes, and ethers were excluded from the chromeleon data export. FAMEs are saturated unless noted otherwise.

```{r, fig.width=8, fig.height=10, warning=FALSE}
# Any necessary limitations to plotted results would go here
plot_results <- results

# Factor the samples to desired order
factored_samples <- c('TC_BAMES_3','SFAMES','SFAMES_F1','SFAMES_F2', 'SFAMES_F3', 'SFAMES_F4', "SFAMES_F5")

plot_results$sample_f = factor(plot_results$sample, levels=factored_samples)

plot_results <- plot_results %>% 
  mutate(fraction_eluent = case_when(
    sample == "TC_BAMES_3" ~ "BAME",
    sample == "SFAMES" ~ "Total Fraction",
    sample == "SFAMES_F1" ~ "F1: 99:1 Hex:Ac (Saturated/Cyclo FAMES)",
    sample == "SFAMES_F2" ~ "F2: 99:2 Hex:Ac (Addl Saturated FAMES)",
    sample == "SFAMES_F3" ~ "F3: 90:10 Hex:Ac (trans, cis monoenes)",
    sample == "SFAMES_F4" ~ "F4: Acetone (dienes)",
    sample == "SFAMES_F5" ~ "F5: 94:6 Acetone:acetonitrile (poly-enes)"
     )
  )

factored_eluents <- c('BAME', "Total Fraction", "F1: 99:1 Hex:Ac (Saturated/Cyclo FAMES)","F2: 99:2 Hex:Ac (Addl Saturated FAMES)","F3: 90:10 Hex:Ac (trans, cis monoenes)", "F4: Acetone (dienes)", "F5: 94:6 Acetone:acetonitrile (poly-enes)")

plot_results$fraction_eluent_f = factor(plot_results$fraction_eluent, levels=factored_eluents)

p_sfames <- plot_results %>%
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`, key = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  facet_wrap(~fraction_eluent_f, ncol = 1, scales = "free_y") +
  ggtitle("Boulder Soil Free FA as FAMES") +
  theme_bw() +
  theme(legend.position = "none")

p_sfames %>% ggplotly(dynamicTicks = TRUE, tooltip = c("key", "x", "y"))
```
